The \project{unRAVE} catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2016-09-09 article/unrave.tex
Leave the specifics out; we will want to refine this selection using our values at respond-to-referee

Using positions, proper motions, and metallicities from the \rave\ official
data release (such that they can be used as comparison), we identify $\sim$160 
probable members of four open clusters that were observed by \rave.  
Upon requiring $(\alpha,\delta) = (51.5^\circ$ to $57.5^\circ$, 21.5$^\circ$ to 28$^\circ)$,
have error in metallicity \texttt{e\_M\_H\_K} $< 0.5$~dex, and radial
velocities between $-10$~km~s$^{-1}$ and 20~km~s$^{-1}$, we identify 78 
Pleiades members.  For the Hyades, by requiring stars within $3.5^\circ$ of the
cluster centre to have: radial velocities between 36~km~s$^{-1}$ and 44~km~s$^{-1}$,
$[{\rm M/H}]_{RAVE}$ within $-0.15$ and 0.35, and \rave\ metallicity errors
$<0.12$~dex, we identify 26 potential members.  Similarly for IC4561 we select
13 stars by requiring: radial velocities within $-20$~km~s$^{-1}$ to $-40$~km~s$^{-1}$,
an error in radial velocity $<3$~km~s$^{-1}$; $[{\rm M/H}]_{RAVE}$ within $-0.15$ and 0.35;
$\alpha$ between $261.1^\circ$ and $261.6^\circ$; and $\delta$ within $-49.7^\circ$
and $-50.1^\circ$.  For the solar-metallicity open cluster member, we 30 select stars solely on
position: $(\alpha,\delta) = (133.1^\circ$ to $132.5^\circ$, $11.6^\circ$ to $12^\circ)$.
We show the effective temperature $\teff$ and surface gravity $\logg$ for these
cluster candidates in Figure \ref{fig:open-cluster-HRD}.  The isochrones are 
sourced from \citet{Bressan_2012}, with cluster properties adopted from 
\cite{Kharchenko_2013}.

>>>>

Using positions, proper motions, and metallicities from the \rave\ official
data release (such that they can be used as comparison), we identify $\sim$160 
probable members of four open clusters that were observed by \rave.
Specifically we identify 78 potential Pleiades members, 26 candidates in the
Hyades, another 13 in IC4561, and 30 stars in the solar-metallicity open
cluster M67.
%Upon requiring $(\alpha,\delta) = (51.5^\circ$ to $57.5^\circ$, 21.5$^\circ$ to 28$^\circ)$,
%have error in metallicity \texttt{e\_M\_H\_K} $< 0.5$~dex, and radial
%velocities between $-10$~km~s$^{-1}$ and 20~km~s$^{-1}$, we identify 78 
%Pleiades members.  For the Hyades, by requiring stars within $3.5^\circ$ of the
%cluster centre to have: radial velocities between 36~km~s$^{-1}$ and 44~km~s$^{-1}$,
%$[{\rm M/H}]_{RAVE}$ within $-0.15$ and 0.35, and \rave\ metallicity errors
%$<0.12$~dex, we identify 26 potential members.  Similarly for IC4561 we select
%13 stars by requiring: radial velocities within $-20$~km~s$^{-1}$ to $-40$~km~s$^{-1}$,
%an error in radial velocity $<3$~km~s$^{-1}$; $[{\rm M/H}]_{RAVE}$ within $-0.15$ and 0.35;
%$\alpha$ between $261.1^\circ$ and $261.6^\circ$; and $\delta$ within $-49.7^\circ$
%and $-50.1^\circ$.  For the solar-metallicity open cluster member, we 30 select stars solely on
%position: $(\alpha,\delta) = (133.1^\circ$ to $132.5^\circ$, $11.6^\circ$ to $12^\circ)$.
We show the effective temperature $\teff$ and surface gravity $\logg$ for these
cluster candidates in Figure \ref{fig:open-cluster-HRD}.  The isochrones are 
sourced from \citet{Bressan_2012}, with cluster properties adopted from 
\cite{Kharchenko_2013}.
